---
title: "Introduction"
date: 2020-04-25 18:13:03
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 2
bibliography: C:/Users/Asus/Desktop/personal_files/advanced_R/advanced_R.bib
---

<style>

body {
text-align: justify}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo      = TRUE, 
                      warning   = FALSE, 
                      message   = FALSE,
                      fig.align = "center")
```

```{r libraries}


```

# Introduction

This section is based on [@wickham_advanced_2019, Chapter 1]

## Why R?

- Free, open source, and available on every major platform

- Diverse and welcoming community: online and in person

    + __[R4DS Online Learning Community](https://www.rfordatasci.com/)__
    
    + __[R-Ladies](https://rladies.org/)__

- Massive set of packages for:

    + Statistical modelling
    
    + Machine learning
    
    + Visualisation
    
    + Importing and manipulating data
    
        + __[CRAN](https://cran.r-project.org/)__ 
        
        + __[Bioconductor](https://www.bioconductor.org/)__

- __[RStudio IDE](https://rstudio.com/products/rstudio/)__ provides an integrated development environment

- There is a company called __[RStudio](https://rstudio.com/)__ whose mission is to create free and open-source software for data science, scientific research, and technical communication

- A strong foundation of functional programming

- Powerful metaprogramming facilities

- The ease with which R can connect to high-performance programming languages like C, Fortran, and C++

### Why R is not perfect?

- Much of the R code you’ll see in the wild is written in haste to solve a pressing problem. This code __isn't__ very: 

    + Elegant
    
    + Fast
    
    + Easy to understand

- Compared to other programming languages, the R community is more focused on results than processes

- Inconsistency is rife across contributed packages, and even within base R

- R is not a particularly fast programming language

## Who should read this book

- Intermediate R programmers who want to dive deeper into R

- Programmers from other languages who are learning R and want to understand how R works

    + You should need to:
    
        + Have written a decent amount of code in R or another programming language
        
            + In the case of R you can start with [@grolemund_hands-programming_2014]
        
        + Be familiar with the basics of data analysis [@wickham_r_2016]:
        
            + Importing
            
            + Wrangling
            
            + Visualizing
            
            + Modeling
            
            + Communicating
            
        + Have written a number of functions
        
        + Be familiar with the installation and use of __[CRAN](https://cran.r-project.org/)__ packages
        
## What you will get out of this book

After reading this book, you will:

- Be familiar with the foundations of R

- Understand what functional programming means, and why it is a useful tool for data science

- Now about R’s rich variety of object-oriented systems:

    + S3
    
    + S4
    
    + S6

- Appreciate the double-edged sword of metaprogramming

- Have a good intuition for which operations in R are slow or use a lot of memory

## What you will not learn

- R as a data analysis tool

    + See [@wickham_r_2016] if you want to learn this

- Build R packages to communicate your code

    + See [@wickham_r_2015] if you want to learn this
    
## Meta-techniques

There are two meta-techniques that are tremendously helpful for improving your skills as an R programmer: 

- Reading source code

    + A great place to start developing this skill is to look at the source code of the functions and packages you use most often

- Adopting a scientific mindset

    + Develop a hypothesis
    
    + Design some experiments and run them
    
    + Record the results

## Recommended reading

- To understand why R’s object systems work see [@abelson_structure_1996]

- To understand the trade-offs that R has made compared to other programming languages see [@van-roy_concepts_2004]

- To learn to be a better programmer see [@hunt_pragmatic_2000]

## Getting help

- __[RStudio Community](https://community.rstudio.com/)__

- __[StackOverflow](https://stackoverflow.com/)__

    + If you want help remember to:

        + Make sure you have the latest version of R and of the package (or packages) you are having problems with

        + Spend some time creating a **repr**oducible **ex**ample (__reprex__)
        
            + See __[reprex](https://CRAN.R-project.org/package=reprex)__

# Bibliography

